%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Chief Technology Officer} % Job title
    {GOMYCODE} % Organization
    {Tunis, Tunisia} % Location
    {Oct. 2017 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Develop technical aspects of the company’s strategy to ensure alignment with its business goals.}
        \item {Supervise system infrastructure to ensure functionality and efficiency.}
        \item {Use stakeholders’ feedback to inform necessary improvements and adjustments to technology.}
        \item {Discover and implement new technologies that yield competitive advantage and help departments use technology profitably.}
        \item {Monitor KPIs and IT budgets to assess technological performance.}
        \item {Build quality assurance and data protection processes.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {GOMYCODE} % Organization
    {Tunis, Tunisia} % Location
    {Oct. 2017 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
\item {Determines operational feasibility by evaluating analysis, problem definition, requirements, solution development, and proposed solutions.}
\item {Documents and demonstrates solutions by developing documentation, flowcharts, layouts, diagrams, charts, code comments and clear code.}
\item {Backend development using ASP.NET Core and Node.JS.}
\item {DevOps (Docker/Kubernetes...) \& Administrating linux systems (CentOS, Ubuntu), configuring servers...}
\item {Configuring and setting up the IT infrastructure (Network, hardware, software).}
\item {Frontend development (ES6, React, Redux, Redux Saga).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Program Manager} % Job title
    {GOMYCODE} % Organization
    {Tunis, Tunisia} % Location
    {Oct. 2017 - Oct. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Guides and manages educational offerings through the launch of a new tracks.}
        \item {Innovates and identifies knowledge gaps and opportunities to develop what is needed to support objectives.}
        \item {Author and implement the Standard Operating Procedures and Emergency Protocols of the program (CP-SOPEP).}
        \item {Oversees all program logistics in support of instructors and participants (including availability
of necessary instructional materials, The Platform, resources and other links, room set-ups, schedules, internet connection, etc.).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Instructor} % Job title
    {GOMYCODE} % Organization
    {Tunis, Tunisia} % Location
    {Aug. 2016 - Mar. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Teach Game Development (C\#, Unity)}
        \item {Lead and manage the instructor team in all tracks (Web, Game, Mobile).}
        \item{Creates and develops curriculum, lesson plans, teaching materials, and Individual Learning Plans to aid students in developing skills and confidence in basic academic areas.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {CoFounder \& Software Developer} % Job title
    {Phexonite} % Organization
    {Tunis, Tunisia} % Location
    {Aug. 2016 - Oct. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {DevOps \& System administration (Linux [CentOS/Debian]).}
        \item {Unity3D game development.}
        \item {Design, Implement, Test and Publish .NET Desktop and Web applications for clients as a freelancer.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Founder \& Software Developer} % Job title
    {Arsslensoft} % Organization
    {Tunisia} % Location
    {Apr. 2010, PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design, Implement, Test and Publish .NET Desktop and Web applications in various fields (e.g: Virtual Assistant, Antivirus, Compiler construction, IDE, Web Browser).}
        \item {PKI \& X509 (Extended validation, code signing, class 1-5 certificate generation according to CA Web browser forum guidelines).}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
