%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Projects}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------
  \cventry
    {Software Developer at Arsslensoft} % Job title
    {OrigiSign Certification Tool} % Organization
    {\href{https://github.com/Arsslensoft/OCT}{Available on Github}} % Location
    {Oct. 2016 - Dec. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {Designed and implemented an interactive GUI PKI management tool in (C\#) based on BouncyCastle and OpenSsl.}
  \item {Custom X509 Extension Visual Programming using ASN.1 Code generation.}
  \item {Supports all standard X.509 and ASN.1 fields and extensions.}
  \item {Integrates an OCSP server based on CRL files.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Software Developer at Arsslensoft} % Job title
    {Developer Studio} % Organization
    {\href{https://github.com/Arsslensoft/Developer-Studio}{Available on Github}} % Location
    {Nov. 2012 - Sep. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {Designed and implemented an integrated development environment in (C\#).}
  \item {Supports plugins and languages integration, code completion, projects, single source file, syntax highlighting, refactoring, visual form designer.}
  \item {Published and maintained multiple editions (i.e: Pascal Edition, Pawn Edition, Professional Edition, Arsslen Language Edition) and multiple versions until version 3 (2013, 2014, 2015).}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Software Developer at Arsslensoft} % Job title
    {Kavprot Smart Security} % Organization
    {\href{https://github.com/Arsslensoft/Kavprot-Smart-Security}{Available on Github}} % Location
    {Oct. 2011 - Jun. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {Designed and implemented a security suite in (C/C++, C\#).}
  \item {Integrated Parental control, Firewall, AntiVirus, Malicious web site protection using proxy interception, File Vault, Heuristics analysis features.}
  \item {Gathered a viral database of 4 Million signatures (ClamAV and other sources).}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Software Developer at Arsslensoft} % Job title
    {Fireweb Navigator} % Organization
    {\href{https://github.com/Arsslensoft/Fireweb-Navigator}{Available on Github}} % Location
    {Sep. 2010 - Aug. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {Designed and implemented a GeckoFx based web browser application in (C\#).}
  \item {Integrated smart search features with a Virtual Assistant.}
  \item {Published and maintained the software until version 9.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Software Developer at Arsslensoft} % Job title
    {VATU Compiler} % Organization
    {\href{https://github.com/Arsslensoft/Vatu}{Available on Github}} % Location
    {Dec. 2015 - Feb. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {Designed and implemented the BNF language grammar.}
  \item {Designed and implemented all the necessary components required to construct the compiler (i.e: Lexer, Parser, Semantic Analyzer, Flow Control, Optimizer, Code generator, Linker) in  (C\#).}
  \item{Implemented a mini kernel based on Vatu language and assembly.} 
  \item {Introduced revolutionary features (e.g: Custom operator symbol definition, Interruption functions, Custom system call conventions).}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}